 Casting multiple shadows: high-dimensional interactive data visualisation with tours and embeddings

### 2020-06-23 paper.Rmd
notes

First, we downloaded the raw mouse retinal single cell RNA-seq data from
@Macosko2015-ot using the `scRNAseq` Bioconductor package [@scRNAseq-d]. We
have followed a standard workflow for pre-processing and normalizing this data 
(described by @Amezquita2020-at): we performed QC using the the `scater`
by removing cells with high proportion of mitocondrial gene expression and low
numbers of genes detected, we log-transformed and normalised the expression 
values and  finally selected highly variable genes (HVGs) using `scran` 
[@McCarthy2017; @Lun2016]. The top ten percent of HVGs were used to subset
the normalised expression matrix and compute PCA using the first 25 components.
Using the PCs we built a shared nearest neighours graph (with k = 10) and 
used Louvain clustering to generate clusters. To check and verify the 
clustering we construct a liminal view. Because most off the variablity in
expression is explained by the first 5 PCs, we tour those. The t-SNE view
is computed from all PCs

- compare to just using the HVGs them selves 
- neighbourhood based brushing to check how diffuse or distorted clusters are
- different distance metrics?

@@

>>>>

First, we downloaded the raw mouse retinal single cell RNA-seq data from
@Macosko2015-ot using the `scRNAseq` Bioconductor package [@scRNAseq-d]. We
have followed a standard workflow for pre-processing and normalizing this data 
(described by @Amezquita2020-at): we performed QC using the the `scater`
by removing cells with high proportion of mitocondrial gene expression and low
numbers of genes detected, we log-transformed and normalised the expression 
values and  finally selected highly variable genes (HVGs) using `scran` 
[@McCarthy2017; @Lun2016]. The top ten percent of HVGs were used to subset
the normalised expression matrix and compute PCA using the first 25 components.
Using the PCs we built a shared nearest neighours graph (with $k = 10$) and 
used Louvain clustering to generate clusters. To check and verify the 
clustering we construct a liminal view. Because most off the variablity in
expression is explained by the first 5 PCs, we tour those. The t-SNE view
is computed from all PCs

- compare to just using the HVGs themselves with the tour
- neighbourhood based brushing to check how diffuse or distorted clusters are
- different distance metrics?

@@

- limitations: large $n$, latency issues
- future work: regularisation tour, slicing and sectioning
